---
title: "Coding Tournament"
author: "Yugdeep"
date: "24 September 2017"
output: html_document
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd("C:/Users/yugde/OneDrive/EPA/EPA1315/Tournament") #Change this directory to where your files are stored
myScriptName <- "myDefector.R"
numberOfrounds <- sample(700:1000, 1) #Value for number of rounds is randomly picked in the range of 700:1000
x = c("cooperate","cooperate","defect","defect")
y = c("cooperate","defect","cooperate","defect")
z = c(4,0,5,2)
w = c(4,5,0,2)
book <- data.frame("id1"=integer(),"id2"=integer(),"tradeno"=integer(),"bid1"=character(),"bid2"=character(), "payoff1"=integer(), "payoff2"=integer())
df <- data.frame("bid1"=x,"bid2"=y, payoff1 = z, payoff2 = w)
```



## Serialize the agents


```{r serializeAgents, echo = FALSE}
fileNames <- list.files()
scriptNames <- fileNames[grep(pattern = "\\.R$", x = fileNames)]
scriptNames <- scriptNames[-grep(pattern = myScriptName, x = scriptNames)]
agent_list <- list()
playing_script_names <- c()
for(i in 1:length(scriptNames)) {
  agentCode <- dget(scriptNames[i])
  agent_list[[i]] <- agentCode$new()
  playing_script_names[i] <- scriptNames[i]
}

# Test agents for functionality
# Remove non-functional agents

numberOfStudentAgents <- length(agent_list)
numberOfMyAgents <- (numberOfStudentAgents %% 2) + 2
for (i in (numberOfStudentAgents+1):(numberOfStudentAgents+numberOfMyAgents)) {
  myAgentCode <- dget(myScriptName)
  agent_list[[i]] <- myAgentCode$new()
  playing_script_names[i] <- myScriptName
}
numberOfTotalAgents <- length(agent_list)
agent_ids <- sample(seq(from = 1, to = numberOfTotalAgents, by = 1))
agent_list <- agent_list[agent_ids]
playing_script_names <- playing_script_names[agent_ids]
for(i in 1:numberOfTotalAgents) {
  cat(playing_script_names[i], "has the ID of", i, "\n")
}
agents_info <- data.frame("agent_id"=c(1:numberOfTotalAgents), "agent_file_name"=playing_script_names, "net_payoff"=NA)
```



## Create the contest


```{r createTournament, echo=FALSE}
# matches are paired opportunities for agents to compete
matches <- c()
for (i in 1:numberOfrounds) {
  
  # There will be an even number of agents, up to about 40
  # each agent has a unique id
  id_list<-1:numberOfTotalAgents
  
  # shuffle the list in place
  shuffle <- sample(id_list)
  
  while (length(shuffle) > 0) {
    
    # get two agents off the list
    el1 <- shuffle[[1]]
    el2 <- shuffle[[2]]
    
    # remove two agents off the front of the list
    shuffle <- shuffle[-1]
    shuffle <- shuffle[-1]
    
    # add your contest to the end of the match list
    matches[[length(matches)+1]] <- c(el1,el2)
    
  }
}
```

`r numberOfTotalAgents` agents are participating in this tournament which will consist of `r numberOfrounds` rounds.

## Run the tournament


Tournament started...

```{r runTournament, echo=FALSE}
# Run the Tournament
# Create the payoff table

x <- length(matches)
# matches is a list of list
# The outer list is a list of contests
# The inner list is a list of two agents

for (i in 1:x) {
  
  # find the first contest
  # get the list, not the slice
  contest <- matches[[i]]
  
  # get the ideas
  id1 <- contest[[1]]
  id2 <- contest[[2]]
  
  # get the agents
  agent1 = agent_list[[id1]]
  agent2 = agent_list[[id2]]
  
  # set the agent ids
  agent1$set_id(id1)
  agent2$set_id(id2)
  
  # set the opponent number
  agent1$set_opponent_id(id2)
  agent2$set_opponent_id(id1)
  
  # set the greetings
  agent1$set_greeting()
  agent2$set_greeting()
  
  # get the greetings
  greeting1 <- agent1$greeting
  greeting2 <- agent2$greeting
  
  #send the greetings
  agent1$receive_greeting(greeting2)
  agent2$receive_greeting(greeting1)
  
  # set the round number
  agent1$set_round(i)
  agent2$set_round(i)
  
  # pass the tournament book
  agent1$set_book(book)
  agent2$set_book(book)
  
  # get the bids
  agent1$get_bid()
  agent2$get_bid()
  
  mybid1 <- agent1$bid
  mybid2 <- agent2$bid
  
  # Run the Tournament
  # record the transaction
  payoffs <-subset(df, bid1 == mybid1 & bid2 == mybid2)
  payoff1 <- payoffs$payoff1
  payoff2 <- payoffs$payoff2
  book = rbind(book,data.frame("id1"=id1,"id2"=id2,"tradeno"= i,"bid1"=mybid1,"bid2"=mybid2,"payoff1"=payoff1,"payoff2"=payoff2))
}
```

## Report results

```{r reportResults, echo=FALSE}
total_payoff <- 0
for(i in 1:numberOfTotalAgents) {
  payoff <- sum((subset(book, i==id1))[["payoff1"]])+sum((subset(book, i==id2))[["payoff2"]])
  cat("Payoff for Agent", i, "(",playing_script_names[i],") is", payoff, "\n")
  total_payoff <- total_payoff + payoff
  agents_info[i,"net_payoff"] <- payoff
}
write.csv2(book,file="bid_register.csv")
write.csv2(agents_info,file="agents_info.csv")
```

Tournament over.


Tournament history has been exported to `bid_register.csv` and `agents_info.csv` files in the current directory.

### Rankings are as follow:

```{r rankings, echo=FALSE}
agents_info[with(agents_info, order(-net_payoff)), ]
```
